Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-23 man/figures/growth_changes.Rmd
adjust sizes

---
output: 
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    highlight: null
    reference_docx: ../../templates/template_pagebreak.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE, dpi = 200)
```

```{r}
library("tidyverse")
library("here")
library("dplyr")
library("ggrepel")
library("scales")
library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
library("magrittr")
```

```{r, echo=FALSE}
show_text <- FALSE
```

**Figure 7.** Comparison of median growth change ($GC$) following @Nowacki1997 for *Q. pyrenaica* sites. Dashed black lines indicate a threshold of 50 % of GC (see material and methods). Note that y-axes do not correspond in all of the three panels for the sake of clarity.

```{r}
gc_todos <- read.csv(here("data/disturbance", "disturbance_gc.csv"), header = TRUE, sep = ',')

# customize plot (corrected scale)
pos_neg_log <- scales::trans_new('signed_log', 
                                 transform = function(x) sign(x)*log(abs(x)),
                                 inverse = function(x) sign(x)*exp(abs(x)))

# Function for plot

@@

  p <- ggplot(df, aes_string(x = x, y = y)) +
    geom_errorbar(mapping = yerrorbar, colour = 'gray', width = .35, size = .3, 
                  na.rm = TRUE) + 
    geom_bar(stat = 'identity', fill = micolor, colour = micolor) +
    geom_hline(yintercept = 0, colour = 'black', lwd = 0.3) + 
    ylab(my_ylab) +
    # Add line to %GC = 50 
    geom_hline(yintercept = c(50, -50), linetype=2, colour='black') +
    theme_bw() +
    theme(panel.grid = element_blank()) +
    coord_cartesian(xlim=limitesX)
    # Customize limits and breaks to min of year data 
  p
}

# ---------- Min and Max axis        
# Get min and max of year range and create vector of 10 years for labelling
xrange <- seq(round(min(gc_todos$year) / 10) * 10, 
    round(max(gc_todos$year) / 10) * 10, by = 10)

@@

# Establece rango de datos para y 
mismo_y <- scale_y_continuous(limits=c(minimoY, maximoY), 
                             breaks = c(-100, -50, 0, 50, 50, 100, 150))

# plots

pcaH <- gc_todos %>% dplyr::filter(site == 'gc_caH') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
         my_ylab = '% GC', micolor = "#838B8B", limitesX = limitesX) + mismo_y +
  scale_x_continuous(breaks = xrange, position = 'bottom') + xlab('') + 
  annotate("text", x = 1990, y = 120, label = "CA-High", fontface = 2, size = 7)

pcaL <- gc_todos %>% dplyr::filter(site == 'gc_caL') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year',
         my_ylab = NULL, micolor = "#838B8B", limitesX = limitesX) +  mismo_y +
  scale_x_continuous(breaks = xrange, position = 'bottom') + 
  annotate("text", x = 1990, y = 120, label = "CA-Low", fontface = 2, size = 7)

psj <- gc_todos %>% dplyr::filter(site == 'gc_sj') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
         my_ylab = NULL, micolor = "#838B8B", limitesX = limitesX) + 
  xlab('') + 
  scale_x_continuous(breaks = xrange, position = 'bottom') + 
  scale_y_continuous(trans = pos_neg_log, 
                     breaks=c(-1000, -500, -100, 1, 100, 500)) + 
  geom_hline(yintercept = 1) +
  annotate("text", x = 1990, y = 450, label = "SJ", fontface = 2, size = 7)

gg <- psj + pcaH + pcaL + 
  plot_layout(ncol=1) & 
  theme(plot.tag = element_text(size = 20, face = 2)) & 
  theme(plot.margin = margin(t=-1,r=3,b=-1,l=3, "pt"))

gg

# gg + plot_annotation(tag_levels = c('a','b', 'c'))

# Ojo ver limites de ylim 
# ggplot_build(pcaL)$layout$panel_params[[1]]$y.range
# ggplot_build(pcaH)$layout$panel_params[[1]]$y.range

@@

>>>>

---
output:
  word_document
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

```{r load_pkg}
library("tidyverse")
library("here")
library("scales")
library("patchwork")
```

**Figure 5.** Comparison of median growth change ($GC$) following @Nowacki1997 for *Q. pyrenaica* sites. Dashed black lines indicate a threshold of 50 % of GC (see material and methods). Note that y-axes do not correspond in all of the three panels for the sake of clarity.

```{r data}
gc_todos <- read.csv(here::here("data/disturbance", "disturbance_gc.csv"), header = TRUE, sep = ',')

# customize plot (corrected scale)
pos_neg_log <- scales::trans_new('signed_log', 
                                 transform = function(x) sign(x)*log(abs(x)),
                                 inverse = function(x) sign(x)*exp(abs(x)))
```

```{r plot_function}
# Function for plot

@@

  p <- ggplot(df, aes_string(x = x, y = y)) +
    geom_errorbar(mapping = yerrorbar, colour = 'gray', width = .35, size = .3, 
                  na.rm = TRUE) + 
    geom_bar(stat = 'identity', fill = micolor, colour = micolor) +
    geom_hline(yintercept = 0, colour = 'black', lwd = 0.3) + 
    ylab(my_ylab) +
    # Add line to %GC = 50 
    geom_hline(yintercept = c(50, -50), linetype=2, colour='black') +
    theme_bw() +
    theme(panel.grid = element_blank(),
          axis.text.y = element_text(size = 5.5),
          axis.text.x = element_text(size = 6)) +
    coord_cartesian(xlim=limitesX)
    # Customize limits and breaks to min of year data 
  p
}

```{r plot_configure}
# ---------- Min and Max axis        
# Get min and max of year range and create vector of 10 years for labelling
xrange <- seq(round(min(gc_todos$year) / 10) * 10, 
    round(max(gc_todos$year) / 10) * 10, by = 10)

@@

# Establece rango de datos para y 
mismo_y <- scale_y_continuous(limits=c(minimoY, maximoY), 
                            breaks = c(-100, -50, 0, 50, 50, 100, 150))
```

```{r plot_caH}
pcaH <- gc_todos %>% dplyr::filter(site == 'gc_caH') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
         my_ylab = '% GC', micolor = "#838B8B", limitesX = limitesX) + mismo_y +
  scale_x_continuous(breaks = xrange, position = 'bottom') + xlab('') + 
  annotate("text", x = 1990, y = 120, label = "CA-High", fontface = 2, size = 3)
```

```{r plot_caL}
pcaL <- gc_todos %>% dplyr::filter(site == 'gc_caL') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year',
         my_ylab = NULL, micolor = "#838B8B", limitesX = limitesX) +  mismo_y +
  scale_x_continuous(breaks = xrange, position = 'bottom') + xlab('Year') + 
  annotate("text", x = 1990, y = 120, label = "CA-Low", fontface = 2, size = 3) 
```

```{r plot_SJ}
psj <- gc_todos %>% dplyr::filter(site == 'gc_sj') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
         my_ylab = NULL, micolor = "#838B8B", limitesX = limitesX) + 
  xlab('') + 
  scale_x_continuous(breaks = xrange, position = 'bottom') + 
  scale_y_continuous(trans = pos_neg_log, 
                     breaks=c(-1000, -500, -100, 1, 100, 500)) + 
  geom_hline(yintercept = 1)+
  annotate("text", x = 1990, y = 440, label = "SJ", fontface = 2, size = 3)

@@

```{r plot_join }
gg <- psj + pcaH + pcaL + 
  plot_layout(ncol=1) & 
  # theme(plot.tag = element_text(size = 12, face = 2)) & 
  theme(plot.margin = margin(t=-1,r=3,b=-1,l=3, "pt"))
```

```{r out_plot, fig.height=5, dpi = 300, out.width = 0.8}
gg

# gg + plot_annotation(tag_levels = c('a','b', 'c'))  
```

### 2018-11-23 man/figures/resilience_long_term.Rmd
adjust sizes

---
output: 
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    highlight: null
    reference_docx: ../../templates/template_pagebreak.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE, dpi = 200)
```

```{r}
library("tidyverse")
library("here")
library("dplyr")
library("ggrepel")
library("scales")
library("grid")
library("gridExtra")
library("patchwork")
library("stringr")
library("pander")
library("lemon")
library("magrittr")
```

```{r, echo=FALSE}
show_text <- FALSE
```

##### 
**Appendix S5.** Resilience metrics of the tree-growth for the most severe drought events (as from Appendix S3). *Left*: Resistance (*Rt*); *Center*: Recovery (*Rc*); *Right* Resilience (*Rs*). Points indicate average of resilience metrics for all populations. Error bar corresponds standard error. Resilience metrics were computed for each population (sample depth > 10) and drought event.

```{r}
df <- read.csv(file=here::here('/out/bai_resiliences_severes' ,'resiliences_bai_droughts.csv'), header=TRUE)

@@

#https://gist.github.com/ottadini/6882677 
lm_eqn = function(m) {
  # Displays regression line equation and R^2 value on plot
  # Usage:
  # p + annotate("text", x=25, y=300, label=lm_eqn(lm(y ~ x, df)), parse=TRUE)

@@

  ggplot(df, aes_string(y=paste0(v, "_mean_mean"), x=x, label=label)) + 
    geom_smooth(method='lm', se=FALSE, colour="black") +
    geom_errorbar(mapping = yerrbar) + 
    geom_point(size=1.5, pch = 21, colour="black", fill="white") + 
    theme_bw() + 
    geom_text_repel(nudge_x = 0.5) + 
    annotate("text", x=coordX_eq, y = coordY_eq, 
             label=lm_eqn(lm(formulita, df)), parse=TRUE, 
             size = 5, fontface = "bold") +
    ggtitle(titulo) + 
    theme(plot.title = element_text(size = 14, face = "bold.italic"),
          panel.grid = element_blank(), 
          axis.text.y = element_text(size=10),
          axis.text.x = element_text(size=9),
          axis.title = element_text(size = 12))
  }

sevRt <- plotrel(sdf, v = "rt", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rt") +
  xlab('') + ylab('')

sevRs <- plotrel(sdf, v = "rs", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rs") + 
  xlab('') + ylab('')

sevRc <- plotrel(sdf, v = "rc", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rc") +
  xlab("Drought Severity") + ylab('')

res_long_term <- sevRt + sevRc + sevRs + plot_layout(nrow = 1)

res_long_term
```

>>>>

---
output:
  word_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

```{r load_pkg}
library("tidyverse")
library("here")
library("scales")
library("patchwork")
library("ggrepel")
```

##### 
**Figure 6.** Resilience metrics of the tree-growth for the most severe drought events (as from Appendix S3). *Left*: Resistance (*Rt*); *Center*: Recovery (*Rc*); *Right* Resilience (*Rs*). Points indicate average of resilience metrics for all populations. Error bar corresponds standard error. Resilience metrics were computed for each population (sample depth > 10) and drought event.

```{r data}
df <- read.csv(file=here::here('/out/bai_resiliences_severes' ,'resiliences_bai_droughts.csv'), header=TRUE)

@@

```

```{r plot_functions}
#https://gist.github.com/ottadini/6882677 
lm_eqn = function(m) {
  # Displays regression line equation and R^2 value on plot
  # Usage:
  # p + annotate("text", x=25, y=300, label=lm_eqn(lm(y ~ x, df)), parse=TRUE)

@@

  ggplot(df, aes_string(y=paste0(v, "_mean_mean"), x=x, label=label)) + 
    geom_smooth(method='lm', se=FALSE, colour="gray") +
    geom_errorbar(mapping = yerrbar) + 
    geom_point(size=1.5, pch = 21, colour="black", fill="white") + 
    theme_bw() + 
    geom_text_repel(nudge_x = 0.5, size = 3) + 
    annotate("text", x=coordX_eq, y = coordY_eq, 
             label=lm_eqn(lm(formulita, df)), parse=TRUE, 
             size = 4, fontface = "bold") +
    ggtitle(titulo) + 
    theme(plot.title = element_text(size = 11, face = "bold.italic"),
          panel.grid = element_blank(), 
          axis.text.y = element_text(size=9),
          axis.text.x = element_text(size=9),
          axis.title = element_text(size = 10))
  }

```

```{r plot_rt}
sevRt <- plotrel(sdf, v = "rt", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rt") +
  xlab('') + ylab('') +
  theme(plot.margin = margin(r=-0.7, l=0, t=0, b=0, "pt"))
```

```{r plot_rs}
sevRs <- plotrel(sdf, v = "rs", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rs") + 
  xlab('') + ylab('') +
  theme(plot.margin = margin(r=0, l=-0.7, t=0, b=0, "pt"))
```

```{r plot_rc}
sevRc <- plotrel(sdf, v = "rc", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rc") +
  xlab("Drought Severity") + ylab('') +
  theme(plot.margin = margin(r=-0.7, l=-0.7, t=0, b=0, "pt"))
```

```{r plot_join}
res_long_term <- sevRt + sevRc + sevRs + 
  plot_layout(nrow = 1) 
```

```{r plot_out, fig.width=6, dpi = 300, out.width = 0.8}
res_long_term
```
